Properties of coronal Fourier power spectra and their implications for coronal seismology and solar atmospheric heating.

### 2014-05-14 tex/paper1/paper1.tex

Each emission event is modeled as an exponentially decaying function
of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and emission $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{total}}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
emission $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the total emission in each event depends on its time scale $T$
such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown that the observed \PS\ can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P_{total}(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}
This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar emission events.

@@

Therefore, the number of effectively independent pixels is less than
the actual number of pixels in any one region.  The number of
effective independent pixels is estimated in the following way.  The
cross correlation $c(\tau)$ function between two randomly chosen
next-nearest neighbor pixels is calculated.  The cross correlation
coefficient measures the linear dependence of two time series $X(t)$
and $Y(t \pm \tau)$ at different lags $\tau$.  This is used to define
a coefficient of independence between next nearest neighbor,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  The
effective number of independent pixels in region is given by
\begin{equation}
\label(eqn:nind}
N_{ind}= 1 + \rho(N_{pixel}-1).
\end{equation}
The number of independent measurements $N$ is set to $N_{ind}$ in
Equation \ref{eqn:errorsigmamean}.  This gives a lengthscale for the
uncertainty in the mean Fourier \PS.

@@

A three step fitting process is used to fit Models 1 and 2 to the
data.
\begin{enumerate}
\item Model 1 is fit to the data using the distribution widths
  $\sigma_{d}$.  Since this is much wider than the estimated error in
  the mean, it allows the fitting algorithm to converge to an
  approximate fit solution.
\item The estimated values to the model parameters are then used as
  initial guesses to the second fit of Model 1, assuming the much
  narrower estimated error $\sigma_{d}/\sqrt{N){ind}$.  This generates
  a better estimate to the parameters of the model fit.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.
\item Model 2 is fit to the data using the distribution widths
  $\sigma_{d}$, seeded with the maximum likelihood parameter values
  from Step 2 and the estimated $G(\nu)$ model parameters from Step 3.
\item Model 2 is fit to the data using the maximum likelihood model
  parameter values at Step 4 and the adjusted widths
  $\sigma_{d}/\sqrt{N){ind}$.
\end{enumarate}

>>>>

Each emission event is modeled as an exponentially decaying function
of time $t$
\begin{equation}
\label{eqn:expdecay}
f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
\end{equation}
for some timescale $T$ and emission $E$.  The corresponding \Fps\ is
\begin{equation}
\label{eqn:ftexpdecay}
P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
\end{equation}
The total \Fps\ along the line of sight is given by
\begin{equation}
\label{eqn:sumftexpdecay}
P_{total}(\nu) = \sum_{T}N(T)P_{T}(\nu)
\end{equation}
where $N(T)$ is the distribution of time-scales for all the events
along the line of sight.  Further, if the number of events of a given
emission $E$ is assumed to be
\begin{equation}
\label{eqn:energydistrib}
N(E) \propto E^{-\alpha_{E}}
\end{equation}
and the total emission in each event depends on its time scale $T$
such that
\begin{equation}
\label{eqn:energytime}
E \propto T^{1+\gamma}
\end{equation}
then it can be shown that the observed \PS\ can be
approximated by
\begin{equation}
\label{eqn:finalfps}
P_{total}(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
\end{equation}
This derivation shows it is possible to generate \PL\ power spectra
using swarms of statistically similar emission events.

@@

Therefore, the number of effectively independent pixels is less than
the actual number of pixels in any one region.  The number of
effective independent pixels is estimated in the following way.  The
cross correlation $c(\tau)$ function between two randomly chosen
next-nearest neighbor pixels is calculated.  The cross correlation
coefficient measures the linear dependence of two time series $X(t)$
and $Y(t \pm \tau)$ at different lags $\tau$.  This is used to define
a coefficient of independence between next nearest neighbor,
\begin{equation}
\label{eqn:ind}
\rho = 1 - \max|c(\tau)|.
\end{equation}
When $\rho$ is 1, the cross-correlation coefficient is zero, and there
is no measurable linear dependence between neighboring time series.
When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
the two time-series are linearly dependent on each other.  The
effective number of independent pixels in region is given by
\begin{equation}
\label{eqn:nind}
N_{ind}= 1 + \rho(N_{pixel}-1).
\end{equation}
The number of independent measurements $N$ is set to $N_{ind}$ in
Equation \ref{eqn:errorsigmamean}.  This gives a lengthscale for the
uncertainty in the mean Fourier \PS.

@@

A three step fitting process is used to fit Models 1 and 2 to the
data.
\begin{enumerate}
\item Model 1 is fit to the data using the distribution widths
  $\sigma_{d}$.  Since this is much wider than the estimated error in
  the mean, it allows the fitting algorithm to converge to an
  approximate fit solution.
\item The estimated values to the model parameters are then used as
  initial guesses to the second fit of Model 1, assuming the much
  narrower estimated error $\sigma_{d}/\sqrt{N}{ind}$.  This generates
  a better estimate to the parameters of the model fit.
\item The residuals of the model 1 fit to the data are then used to
  estimate the model parameters of $G(\nu)$.
\item Model 2 is fit to the data using the distribution widths
  $\sigma_{d}$, seeded with the maximum likelihood parameter values
  from Step 2 and the estimated $G(\nu)$ model parameters from Step 3.
\item Model 2 is fit to the data using the maximum likelihood model
  parameter values at Step 4 and the adjusted widths
  $\sigma_{d}/\sqrt{N}{ind}$.
\end{enumerate}
